---
title: "Untitled"
author: "HELENA GIL BUITRAGO"
date: "2025-02-11"
output: html_document
---
#Library
```{r}
library(tidyverse)

file <- "C:\\Social Brain Lab\\VALAWAI\\Behavioural R\\Study Trust.csv"

data <- read.csv(file = file, sep = ",")
data <- data[-c(1:89), ]

# Delete participats that did not pay attention
data_filtrada <- data %>%
  filter(if_all(26:38, ~ is.na(.) | . == "") | AttentionCheck2 == 5) %>% select(19,20:21,23,39:177)
```
#Cleaning and preparing data
```{r}
bloques <- list(
  UP = c("Acuerdo1_UP", "Acuerdo2_UP", "Acuerdo3_UP", "Acuerdo4_UP"),
  UR = c("Acuerdo5_UR", "Acuerdo6_UR", "Acuerdo7_UR", "Acuerdo8_UR"),
  CP = c("Acuerdo1_CP", "Acuerdo2_CP", "Acuerdo3_CP", "Acuerdo4_CP"),
  CR = c("Acuerdo5_CR", "Acuerdo6_CR", "Acuerdo7_CR", "Acuerdo8_CR"),
  DP = c("Acuerdo1_DP", "Acuerdo2_DP", "Acuerdo3_DP", "Acuerdo4_DP"),
  DR = c("Acuerdo5_DR", "Acuerdo6_DR", "Acuerdo7_DR", "Acuerdo8_DR"),
  NMP = c("Acuerdo1_NMP", "Acuerdo2_NMP", "Acuerdo3_NMP", "Acuerdo4_NMP"),
  NMR = c("Acuerdo5_NMR", "Acuerdo6_NMR", "Acuerdo7_NMR", "Acuerdo8_NMR")
)

# "Acuerdo" to numeric
for (bloque in names(bloques)) {
  acuerdo_cols <- bloques[[bloque]]
  data_filtrada[acuerdo_cols] <- lapply(data_filtrada[acuerdo_cols], as.numeric)
}

# Select y convert the rets to numeric
cols_to_convert <- data_filtrada %>%
  select(starts_with("Reliability"), starts_with("MoralAgency"),
         starts_with("MoralTrust"), starts_with("IS_"), starts_with("Complejidad"), starts_with("Antro")) %>%
  colnames()

data_filtrada[cols_to_convert] <- lapply(data_filtrada[cols_to_convert], as.numeric)

#Convert Direction to numeric (Direct == 0, Inverse == 1)
data_filtrada <- data_filtrada %>%
  mutate(across(
    starts_with("Direction_"), 
    ~ ifelse(. == "Direct", 0, ifelse(. == "Inverse", 1, NA_real_))
  ))

#Reverse score
matriz_IS <- data_filtrada %>% select(contains("IS"))
matriz_direction <- data_filtrada %>% select(contains("Direction"))

# Adjust scores (if Direction == 1, - to 100)
matriz_IS_adjusted <- matriz_IS
for (i in 1:ncol(matriz_IS)) {
  matriz_IS_adjusted[[i]] <- ifelse(matriz_direction[[i]] == 1, 
                                     100 - matriz_IS[[i]], 
                                     matriz_IS[[i]])
}

data2_filtered <- data_filtrada %>%
  select(-c(23:30, 49:56, 75:82, 101:108, 112:143))
combined_data <- bind_cols(data2_filtered, matriz_IS_adjusted)


#Cleaning
colnames(combined_data) <- colnames(combined_data) %>%
  gsub("_1$", "", .) 

combined_data <- combined_data %>%
  rename(IS_UR_1 = IS_UR_1.)
combined_data <- combined_data %>%
  rename_with(~ gsub("IS_(.*)_(\\d+)", "IS\\2_\\1", .), starts_with("IS_"))

colnames(combined_data)

# Mean "Acuerdo"
data_media_acuerdo <- combined_data %>%
  mutate(
    media_acuerdo_UP = rowMeans(select(., all_of(bloques$UP)), na.rm = TRUE),
    media_acuerdo_UR = rowMeans(select(., all_of(bloques$UR)), na.rm = TRUE),
    media_acuerdo_CP = rowMeans(select(., all_of(bloques$CP)), na.rm = TRUE),
    media_acuerdo_CR = rowMeans(select(., all_of(bloques$CR)), na.rm = TRUE),
    media_acuerdo_DP = rowMeans(select(., all_of(bloques$DP)), na.rm = TRUE),
    media_acuerdo_DR = rowMeans(select(., all_of(bloques$DR)), na.rm = TRUE),
    media_acuerdo_NMP = rowMeans(select(., all_of(bloques$NMP)), na.rm = TRUE),
    media_acuerdo_NMR = rowMeans(select(., all_of(bloques$NMR)), na.rm = TRUE)
  )

#Mean "IS"
data_media_IS <- data_media_acuerdo %>%
  mutate(
    media_IS_UR = rowMeans(select(., starts_with("IS") & ends_with("UR")), na.rm = TRUE),
    media_IS_CR = rowMeans(select(., starts_with("IS") & ends_with("CR")), na.rm = TRUE),
    media_IS_DR = rowMeans(select(., starts_with("IS") & ends_with("DR")), na.rm = TRUE),
    media_IS_NMR = rowMeans(select(., starts_with("IS") & ends_with("NMR")), na.rm = TRUE)
  )

#Delete unnecessary columns
data_cleaned <- data_media_IS %>%
  select(-c(78:111))
```

#Creating data_long
```{r}
Group <- rep(c("UP", "UR", "CP", "CR", 
           "DP", "DR", "NMP", "NMR"), times = 249) 

############################ Long Reliability ############################
df_reliability <- data_cleaned %>%
    select(identity, starts_with("Reliability")) %>%
  pivot_longer(
    cols = starts_with("Reliability"),  
    names_to = "Scale",  
    values_to = "Reliability"  
  ) %>%
  cbind(., Group) %>%
select(-Scale)

############################ Long Moral Agency ############################
df_agency <- data_cleaned %>%
    select(identity, starts_with("MoralAgency")) %>%
  pivot_longer(
    cols = starts_with("MoralAgency"),  
    names_to = "Scale",  
    values_to = "MoralAgency"  
  ) %>%
  cbind(., Group) %>%
select(-Scale)

############################ Long Moral Trust ############################
df_trust <- data_cleaned %>%
    select(identity, starts_with("MoralTrust")) %>%
  pivot_longer(
    cols = starts_with("MoralTrust"),  
    names_to = "Scale",  
    values_to = "MoralTrust"  
  ) %>%
  cbind(., Group) %>%
select(-Scale)

############################ Long Complexity ############################
df_complexity <- data_cleaned %>%
    select(identity, starts_with("Complexity")) %>%
  pivot_longer(
    cols = starts_with("Complexity"),  
    names_to = "Scale",  
    values_to = "Complexity"  
  ) %>%
  cbind(., Group) %>%
select(-Scale)


############################ Long agreement ############################
df_agreement <- data_cleaned %>%
    select(identity, starts_with("media_acuerdo")) %>%
  pivot_longer(
    cols = starts_with("media_acuerdo"),  
    names_to = "Scale",  
    values_to = "Acuerdo"  
  ) %>%
  cbind(., Group) %>%
select(-Scale)


Group_R <- rep(c("UR", "CR", "DR", "NMR"), times = 249) 
############################ Long Antro ############################
df_antroH <- data_cleaned %>%
    select(identity, starts_with("AntroH")) %>%
  pivot_longer(
    cols = starts_with("AntroH"),  
    names_to = "Scale",  
    values_to = "AntroH"  
  ) %>%
  cbind(., Group_R) %>%
select(-Scale)

df_antroR <- data_cleaned %>%
    select(identity, starts_with("AntroR")) %>%
  pivot_longer(
    cols = starts_with("AntroR"),  
    names_to = "Scale",  
    values_to = "AntroR"  
  ) %>%
  cbind(., Group_R) %>%
select(-Scale)


############################ Long Intentional Stance ############################
df_IS <- data_cleaned %>%
    select(identity, starts_with("media_IS")) %>%
  pivot_longer(
    cols = starts_with("media_IS"),  
    names_to = "Scale",  
    values_to = "IS"  
  ) %>%
  cbind(., Group_R) %>%
select(-Scale)
```

#Alpha
```{r}
library(psych)
head(df_IS)

df_wide <- df_IS %>%
  pivot_wider(names_from = Group_R, values_from = IS)

df_wide <- df_wide %>%
  select(UR, CR, DR, NMR) %>%
  mutate(across(everything(), as.numeric))

alpha_IS <- alpha(df_wide)
summary(alpha_IS)
```


#Merge long_df
```{r}
library(dplyr)
library(tidyr)
library(purrr)

grupos_todos <- c("UP", "UR", "CP", "CR", "DP", "DR", "NMP", "NMR")

grupos_reducidos <- c("UR", "CR", "DR", "NMR")

add_group <- function(df, group_list) {
  df %>%
    group_by(identity) %>%
    mutate(Group = rep(group_list, length.out = n())) %>%
    ungroup()
}

df_reliability <- data_cleaned %>%
  select(identity, starts_with("Reliability")) %>%
  pivot_longer(cols = starts_with("Reliability"), names_to = "Scale", values_to = "Reliability") %>%
  add_group(grupos_todos) %>%
  select(-Scale)

df_agency <- data_cleaned %>%
  select(identity, starts_with("MoralAgency")) %>%
  pivot_longer(cols = starts_with("MoralAgency"), names_to = "Scale", values_to = "MoralAgency") %>%
  add_group(grupos_todos) %>%
  select(-Scale)

df_trust <- data_cleaned %>%
  select(identity, starts_with("MoralTrust")) %>%
  pivot_longer(cols = starts_with("MoralTrust"), names_to = "Scale", values_to = "MoralTrust") %>%
  add_group(grupos_todos) %>%
  select(-Scale)

df_complexity <- data_cleaned %>%
  select(identity, starts_with("Complexity")) %>%
  pivot_longer(cols = starts_with("Complexity"), names_to = "Scale", values_to = "Complexity") %>%
  add_group(grupos_todos) %>%
  select(-Scale)

df_agreement <- data_cleaned %>%
  select(identity, starts_with("media_acuerdo")) %>%
  pivot_longer(cols = starts_with("media_acuerdo"), names_to = "Scale", values_to = "acuerdo") %>%
  add_group(grupos_todos) %>%
  select(-Scale)

df_antroH <- data_cleaned %>%
  select(identity, starts_with("AntroH")) %>%
  pivot_longer(cols = starts_with("AntroH"), names_to = "Scale", values_to = "AntroH") %>%
  add_group(grupos_reducidos) %>%
  select(-Scale)

df_antroR <- data_cleaned %>%
  select(identity, starts_with("AntroR")) %>%
  pivot_longer(cols = starts_with("AntroR"), names_to = "Scale", values_to = "AntroR") %>%
  add_group(grupos_reducidos) %>%
  select(-Scale)

df_IS <- data_cleaned %>%
  select(identity, starts_with("media_IS")) %>%
  pivot_longer(cols = starts_with("media_IS"), names_to = "Scale", values_to = "IS") %>%
  add_group(grupos_reducidos) %>%
  select(-Scale)

base_identity <- expand_grid(
  identity = unique(data_cleaned$identity),
  Group = grupos_todos
)

merge_list <- list(df_reliability, df_agency, df_trust, df_complexity, df_agreement, df_antroH, df_antroR, df_IS)
merge_list <- map(merge_list, ~ full_join(base_identity, .x, by = c("identity", "Group")))

# Merge 
df_combined <- reduce(merge_list, full_join, by = c("identity", "Group")) %>%
  arrange(identity, Group)

#Add framework and type of agent
df_combined <- df_combined %>%
  mutate(
    type = case_when(
      Group %in% c("UP", "CP", "DP", "NMP") ~ "Person",
      Group %in% c("UR", "CR", "DR", "NMR") ~ "Robot",
      TRUE ~ NA_character_
    ),
    framework = case_when(
      Group %in% c("UP", "UR") ~ "Utilitarianism",
      Group %in% c("CP", "CR") ~ "Contractualism",
      Group %in% c("DP", "DR") ~ "Deontology",
      Group %in% c("NMP", "NMR") ~ "NonMoral",
      TRUE ~ NA_character_
    )
  )

```

#Reference group
```{r}
data_long <- df_combined %>%
  mutate(
    framework = relevel(as.factor(framework), ref = "NonMoral"),
    type = relevel(as.factor(type), ref = "Person")
  )

```

#Reliability
```{r}
library(lmerTest)
library(emmeans)

# Mixed Model for Reliability
modelo_reliability <- lmer(Reliability ~ framework + type + acuerdo + (1 | identity), 
                            data = df_combined)
summary(modelo_reliability)
confint(modelo_reliability, level = 0.95) 

int_reliability <- lmer(Reliability ~ framework * type + acuerdo + (1 | identity), 
                            data = df_combined)
summary(int_reliability)
confint(int_reliability, level = 0.95)

emmeans_moralreliability <- emmeans(int_reliability, pairwise ~ type | framework)
summary(emmeans_moralreliability)
confint(emmeans_moralreliability, level = 0.95)

library(ggplot2)
library(dplyr)
library(ggpubr)


# CI
summary(emmeans_moralreliability, confint = TRUE, scale = TRUE, transform.response = T, digits = getOption("jtools-digits", 3))

# Emmeans
emtab <- emmeans(emmeans_moralreliability, ~ framework | type )
emtab <- as_tibble(emtab)

type_colors <- c(
  "Person" = "#FF637D",  
  "Robot" = "#4682B4"  
)

emtab <- regrid(emmeans(emmeans_moralreliability, ~ framework | type)) %>%
  as_tibble()

# Graph
ggplot(emtab, aes(x = framework, y = emmean, color = type)) + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                position = position_dodge(0.5), width = 0.25) + 
  geom_point(size = 3, position = position_dodge(0.5), shape = 16) +  
  scale_color_manual(values = type_colors, name = NULL) +  
  theme_minimal() + 
  labs(x = "Framework", y = "Reliability") +
  scale_y_continuous(limits = c(1, 7), breaks = 1:7) +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))

#Aumented Graph
ggplot(emtab, aes(x = framework, y = emmean, color = type)) + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                position = position_dodge(0.5), width = 0.25) + 
  geom_point(size = 3, position = position_dodge(0.5), shape = 16) +  
  scale_color_manual(values = type_colors, name = NULL) +  
  theme_minimal() + 
  labs(x = "Framework", y = "Reliability") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))
```

#Moral Trust
```{r}
# Mixed Model for MoralTrust
modelo_moraltrust <- lmer(MoralTrust ~ framework + type + acuerdo + (1 | identity), 
                            data = data_long)
summary(modelo_moraltrust)
confint(modelo_moraltrust, level = 0.95)

int_moraltrust <- lmer(MoralTrust ~ framework * type + acuerdo + (1 | identity), 
                            data = df_combined)
summary(int_moraltrust)
confint(int_moraltrust, level = 0.95)

emmeans_moraltrust <- emmeans(int_moraltrust, pairwise ~ type | framework)
summary(emmeans_moraltrust)
confint(emmeans_moraltrust, level = 0.95)

# CI
summary(emmeans_moraltrust, confint = TRUE, scale = TRUE, transform.response = T, digits = getOption("jtools-digits", 3))

# Emmeans
emtab <- emmeans(emmeans_moraltrust, ~ framework | type )
emtab <- as_tibble(emtab)

type_colors <- c(
  "Person" = "#FF637D",  
  "Robot" = "#4682B4"   
)

emtab <- regrid(emmeans(emmeans_moraltrust, ~ framework | type)) %>%
  as_tibble()

# Graph
ggplot(emtab, aes(x = framework, y = emmean, color = type)) + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                position = position_dodge(0.5), width = 0.25) + 
  geom_point(size = 3, position = position_dodge(0.5), shape = 16) +  
  scale_color_manual(values = type_colors, name = NULL) +  
  theme_minimal() + 
  labs(x = "Framework", y = "Moral Trust") +
  scale_y_continuous(limits = c(1, 7), breaks = 1:7) +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))

#Aumented graph
ggplot(emtab, aes(x = framework, y = emmean, color = type)) + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                position = position_dodge(0.5), width = 0.25) + 
  geom_point(size = 3, position = position_dodge(0.5), shape = 16) +  
  scale_color_manual(values = type_colors, name = NULL) +  
  theme_minimal() + 
  labs(x = "Framework", y = "Moral Trust") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))
```

#Moral Agency
```{r}
# Miex model for MoralAgency
modelo_moralagency <- lmer(MoralAgency ~ framework + type + acuerdo + (1 | identity), 
                            data = data_long)
summary(modelo_moralagency)
confint(modelo_moralagency, level = 0.95)

int_moralagency <- lmer(MoralAgency ~ framework * type + acuerdo + (1 | identity), 
                            data = df_combined)
summary(int_moralagency)

emmeans_moralagency <- emmeans(int_moralagency, pairwise ~ framework | type)
summary(emmeans_moralagency)

# CI
summary(emmeans_moralagency, confint = TRUE, scale = TRUE, transform.response = T, digits = getOption("jtools-digits", 3))

# Emmeans
emtab <- emmeans(emmeans_moralagency, ~ framework | type )
emtab <- as_tibble(emtab)

type_colors <- c(
  "Person" = "#FF637D",  
  "Robot" = "#4682B4"    
)

emtab <- regrid(emmeans(emmeans_moralagency, ~ framework | type)) %>%
  as_tibble()

# Graph
ggplot(emtab, aes(x = framework, y = emmean, color = type)) + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                position = position_dodge(0.5), width = 0.25) + 
  geom_point(size = 3, position = position_dodge(0.5), shape = 16) +  
  scale_color_manual(values = type_colors, name = NULL) +  
  theme_minimal() + 
  labs(x = "Framework", y = "Moral Agency") +
  scale_y_continuous(limits = c(1, 7), breaks = 1:7) +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))

#Aumented graph
ggplot(emtab, aes(x = framework, y = emmean, color = type)) + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                position = position_dodge(0.5), width = 0.25) + 
  geom_point(size = 3, position = position_dodge(0.5), shape = 16) +  
  scale_color_manual(values = type_colors, name = NULL) +  
  theme_minimal() + 
  labs(x = "Framework", y = "Moral Agency") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))
```

#Complexity
```{r}
data_long$Complexity <- as.numeric(data_long$Complexity)
df_combined$Complexity <- as.numeric(df_combined$Complexity)

# Mixed model Complexity
modelo_Complejidad <- lmer(Complexity ~ framework + type + acuerdo + (1 | identity), 
                            data = df_combined)
summary(modelo_Complejidad)
confint(modelo_Complejidad, level = 0.95)

int_Complejidad <- lmer(Complexity ~ framework * type + acuerdo + (1 | identity), 
                            data = df_combined)
summary(int_Complejidad)

emmeans_moralcomplejidad <- emmeans(int_Complejidad, pairwise ~ framework | type)
summary(emmeans_moralcomplejidad)

# CI
summary(emmeans_moralcomplejidad, confint = TRUE, scale = TRUE, transform.response = T, digits = getOption("jtools-digits", 3))

# Emmeans
emtab <- emmeans(emmeans_moralcomplejidad, ~ framework | type )
emtab <- as_tibble(emtab)

type_colors <- c(
  "Person" = "#FF637D",  
  "Robot" = "#4682B4"   
)

emtab <- regrid(emmeans(emmeans_moralcomplejidad, ~ framework | type)) %>%
  as_tibble()

# Graph
ggplot(emtab, aes(x = framework, y = emmean, color = type)) + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                position = position_dodge(0.5), width = 0.25) + 
  geom_point(size = 3, position = position_dodge(0.5), shape = 16) +  
  scale_color_manual(values = type_colors, name = NULL) +  
  theme_minimal() + 
  labs(x = "Framework", y = "Complexity") +
  scale_y_continuous(limits = c(1, 7), breaks = 1:7) +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))

#Aumented graph
ggplot(emtab, aes(x = framework, y = emmean, color = type)) + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                position = position_dodge(0.5), width = 0.25) + 
  geom_point(size = 3, position = position_dodge(0.5), shape = 16) +  
  scale_color_manual(values = type_colors, name = NULL) +  
  theme_minimal() + 
  labs(x = "Framework", y = "Complexity") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))
```

#IS
```{r}
#Mean IS
mean_IS <- df_combined %>%
  summarise(
    mean_IS = mean(IS, na.rm = TRUE),
    sd_IS = sd(IS, na.rm = TRUE)
  )
summary(mean_IS)


# Mixed model for IS
modelo_IS <- lmer(IS ~ framework + acuerdo + (1 | identity), 
                            data = df_combined)
summary(modelo_IS)
confint(modelo_IS, level = 0.95)

int_IS <- lmer(IS ~ framework * acuerdo + (1 | identity), 
                            data = df_combined)
summary(int_IS)

emmeans_moralIS <- emmeans(modelo_IS, pairwise ~ framework)
summary(emmeans_moralIS)

# Emmeans
emmeans_moralIS <- emmeans(int_IS, pairwise ~ framework)
summary(emmeans_moralIS)

# CI
summary(emmeans_moralIS, confint = TRUE, scale = TRUE, transform.response = T, digits = getOption("jtools-digits", 3))

# Emmeans for framework
emtab <- emmeans(emmeans_moralIS, ~ framework)

emtab <- regrid(emtab) %>% as_tibble()


type_colors <- c(
  "Person" = "#FF637D",  
  "Robot" = "#4682B4"    
)

# Graph
ggplot(emtab, aes(x = framework, y = emmean, color = "Robot")) + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                width = 0.25) + 
  geom_point(size = 3, shape = 16) +  
  scale_color_manual(values = type_colors, name = NULL) + 
  theme_minimal() + 
  labs(
    x = "Framework", 
    y = "Intentional Stance") +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))

# Aumented graph
ggplot(emtab, aes(x = framework, y = emmean, color = "Robot")) + 
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), 
                width = 0.25) + 
  geom_point(size = 3, shape = 16) +  
  scale_color_manual(values = type_colors, name = NULL) + 
  theme_minimal() + 
  labs(
    x = "Framework", 
    y = "Intentional Stance") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))
```

#Anthropomorphism basic analysis
```{r}
library(mediation)
library(lavaan)

#Anthropomorphism 
modelo_antroH <- lmer(AntroH ~ framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(modelo_antroH)

emmeans_antroH <- emmeans(modelo_antroH, pairwise ~ framework)
summary(emmeans_antroH)

modelo_mediador_H <- lmer(MoralTrust ~ framework + AntroH + (1 | identity),
                          data = df_combined)
summary(modelo_mediador_H)

modelo1 <- lm(AntroH ~ framework, data = df_combined)

modelo2 <- lm(MoralTrust ~ framework + AntroH + acuerdo, data = df_combined)

mediate_test <- mediate(modelo1, modelo2, treat = "framework", mediator = "AntroH", boot = TRUE, sims = 500)
summary(mediate_test)



#Robotization
modelo_antroR <- lmer(AntroR ~ framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(modelo_antroR)

emmeans_antroR <- emmeans(modelo_antroR, pairwise ~ framework)
summary(emmeans_antroR)

modelo_mediador_R <- lmer(MoralTrust ~ framework + AntroR + (1 | identity),
                          data = df_combined)
summary(modelo_mediador_R)

modelo1 <- lm(AntroR ~ framework, data = df_combined)

modelo2 <- lm(MoralTrust ~ framework + AntroR + acuerdo, data = df_combined)

mediate_test_R <- mediate(modelo1, modelo2, treat = "framework", mediator = "AntroR", boot = TRUE, sims = 500)
summary(mediate_test_R)

```

#Correlations Antropomorphism-direct variables
```{r}
###############################AntroH################################
###Controling by framework
reliability_antroH <- lmer(Reliability ~ AntroH + framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(reliability_antroH)
confint(reliability_antroH, level = 0.95) 

trust_antroH <- lmer(MoralTrust ~ AntroH + framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(trust_antroH)
confint(trust_antroH, level = 0.95) 

agency_antroH <- lmer(MoralAgency ~ AntroH + framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(agency_antroH)
confint(agency_antroH, level = 0.95) 

complexity_antroH <- lmer(Complexity ~ AntroH + framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(complexity_antroH)
confint(complexity_antroH, level = 0.95) 

IS_antroH <- lmer(IS ~ AntroH + framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(IS_antroH)
confint(IS_antroH, level = 0.95) 

#####AntroR

reliability_antroR <- lmer(Reliability ~ AntroR + framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(reliability_antroR)
confint(reliability_antroR, level = 0.95) 

trust_antroR <- lmer(MoralTrust ~ AntroR + framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(trust_antroR)
confint(trust_antroR, level = 0.95) 

agency_antroR <- lmer(MoralAgency ~ AntroR + framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(agency_antroR)
confint(agency_antroHR, level = 0.95) 

complexity_antroR <- lmer(Complexity ~ AntroR + framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(complexity_antroR)
confint(complexity_antroR, level = 0.95)

IS_antroR <- lmer(IS ~ AntroR + framework + acuerdo + (1 | identity),
                      data = df_combined)
summary(IS_antroR)
confint(IS_antroR, level = 0.95)

####Correlation without controling by framework 
#Acuerdo AntroH
cor.test(df_combined$acuerdo[df_combined$type == "Robot"], df_combined$AntroH[df_combined$type == "Robot"])

#Reliability AntroH
cor.test(df_combined$Reliability[df_combined$type == "Robot"], df_combined$AntroH[df_combined$type == "Robot"])

#Moral Trust AntroH
cor.test(df_combined$MoralTrust[df_combined$type == "Robot"], df_combined$AntroH[df_combined$type == "Robot"])

#Moral Agency AntroH
cor.test(df_combined$MoralAgency[df_combined$type == "Robot"], df_combined$AntroH[df_combined$type == "Robot"])

#Complexity AntroH
df_combined$Complexity <- as.numeric(as.character(df_combined$Complexity))
cor.test(df_combined$Complexity[df_combined$type == "Robot"], df_combined$AntroH[df_combined$type == "Robot"])

#IS AntroH
cor.test(df_combined$IS[df_combined$type == "Robot"], df_combined$AntroH[df_combined$type == "Robot"])

###############################AntroR################################

#Acuerdo AntroR
cor.test(df_combined$acuerdo[df_combined$type == "Robot"], df_combined$AntroR[df_combined$type == "Robot"])

#Reliability AntroR
cor.test(df_combined$Reliability[df_combined$type == "Robot"], df_combined$AntroR[df_combined$type == "Robot"])

#Moral Trust AntroR
cor.test(df_combined$MoralTrust[df_combined$type == "Robot"], df_combined$AntroR[df_combined$type == "Robot"])

#Moral Agency AntroR
cor.test(df_combined$MoralAgency[df_combined$type == "Robot"], df_combined$AntroR[df_combined$type == "Robot"])

#Complexity AntroR
df_combined$Complexity <- as.numeric(as.character(df_combined$Complexity))
cor.test(df_combined$Complexity[df_combined$type == "Robot"], df_combined$AntroR[df_combined$type == "Robot"])

#IS AntroR
cor.test(df_combined$IS[df_combined$type == "Robot"], df_combined$AntroR[df_combined$type == "Robot"])

#########Table#####################
library(dplyr)
library(tidyr)

cor_results <- data.frame(
  Variable = character(),
  Correlation = numeric(),
  Antro_Type = character(),
  stringsAsFactors = FALSE
)

# Variables to correlate
variables <- c("acuerdo", "Reliability", "MoralTrust", "MoralAgency", "Complexity", "IS")

# Run correlations
run_correlation <- function(var, target) {
  test <- cor.test(df_combined[[var]][df_combined$type == "Robot"], 
                   df_combined[[target]][df_combined$type == "Robot"])
  return(data.frame(Variable = var, Correlation = test$estimate, Antro_Type = target))
}

# Correlations for AntroH and AntroR
for (var in variables) {
  cor_results <- bind_rows(cor_results, run_correlation(var, "AntroH"))
  cor_results <- bind_rows(cor_results, run_correlation(var, "AntroR"))
}

# Table
corr_table <- cor_results %>% arrange(Antro_Type, Variable)
summary(corr_table)

```


#Mediation Analysis Contractualism vs Utilitarianism
```{r}
detach("package:lmerTest", unload=TRUE)
library(mediation)
#Reliability
df2 <- df_combined[(df_combined$framework=="Contractualism" | df_combined$framework=="Utilitarianism"),]
 
modelo_antroH <- lmer(AntroH ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroH)
 
modelo_mediador_H_reli <- lmer(Reliability ~ framework + AntroH + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_H_reli)
 
mediate_test <- mediate(modelo_antroH, modelo_mediador_H_reli, treat = "framework",
    mediator = "AntroH", boot = FALSE, sims = 2000)
summary(mediate_test)

#MoralTrust
df2 <- df_combined[(df_combined$framework=="Contractualism" | df_combined$framework=="Utilitarianism"),]
 
modelo_antroH <- lmer(AntroH ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroH)
 
modelo_mediador_H_trust <- lmer(MoralTrust ~ framework + AntroH + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_H_trust)
 
mediate_test <- mediate(modelo_antroH, modelo_mediador_H_trust, treat = "framework",
    mediator = "AntroH", boot = FALSE, sims = 2000)
summary(mediate_test)

#MoralAgency
df2 <- df_combined[(df_combined$framework=="Contractualism" | df_combined$framework=="Utilitarianism"),]
 
modelo_antroH <- lmer(AntroH ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroH)
 
modelo_mediador_H_agency <- lmer(MoralAgency ~ framework + AntroH + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_H_agency)
 
mediate_test <- mediate(modelo_antroH, modelo_mediador_H_agency, treat = "framework",
    mediator = "AntroH", boot = FALSE, sims = 2000)
summary(mediate_test)

```

#Mediation Analysis Contractualism vs Deontology
```{r}
#detach("package:lmerTest", unload=TRUE)
#Reliability
df2 <- df_combined[(df_combined$framework=="Contractualism" | df_combined$framework=="Deontology"),]
 
modelo_antroH <- lmer(AntroH ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroH)
 
modelo_mediador_H_reli <- lmer(Reliability ~ framework + AntroH + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_H_reli)
 
mediate_test <- mediate(modelo_antroH, modelo_mediador_H_reli, treat = "framework",
    mediator = "AntroH", boot = FALSE, sims = 2000)
summary(mediate_test)

#MoralTrust
df2 <- df_combined[(df_combined$framework=="Contractualism" | df_combined$framework=="Deontology"),]
 
modelo_antroH <- lmer(AntroH ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroH)
 
modelo_mediador_H_trust <- lmer(MoralTrust ~ framework + AntroH + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_H_trust)
 
mediate_test <- mediate(modelo_antroH, modelo_mediador_H_trust, treat = "framework",
    mediator = "AntroH", boot = FALSE, sims = 2000)
summary(mediate_test)

#MoralAgency
df2 <- df_combined[(df_combined$framework=="Contractualism" | df_combined$framework=="Deontology"),]
 
modelo_antroH <- lmer(AntroH ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroH)
 
modelo_mediador_H_agency <- lmer(MoralAgency ~ framework + AntroH + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_H_agency)
 
mediate_test <- mediate(modelo_antroH, modelo_mediador_H_agency, treat = "framework",
    mediator = "AntroH", boot = FALSE, sims = 2000)
summary(mediate_test)
```

#Mediation Analysis Deontology vs Utilitarianism
```{r}
#detach("package:lmerTest", unload=TRUE)
#Reliability
df2 <- df_combined[(df_combined$framework=="Utilitarianism" | df_combined$framework=="Deontology"),]
 
modelo_antroH <- lmer(AntroH ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroH)
 
modelo_mediador_H_reli <- lmer(Reliability ~ framework + AntroH + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_H_reli)
 
mediate_test <- mediate(modelo_antroH, modelo_mediador_H_reli, treat = "framework",
    mediator = "AntroH", boot = FALSE, sims = 2000)
summary(mediate_test)

#MoralTrust
df2 <- df_combined[(df_combined$framework=="Utilitarianism" | df_combined$framework=="Deontology"),]
 
modelo_antroH <- lmer(AntroH ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroH)
 
modelo_mediador_H_trust <- lmer(MoralTrust ~ framework + AntroH + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_H_trust)
 
mediate_test <- mediate(modelo_antroH, modelo_mediador_H_trust, treat = "framework",
    mediator = "AntroH", boot = FALSE, sims = 2000)
summary(mediate_test)

#MoralAgency
df2 <- df_combined[(df_combined$framework=="Utilitarianism" | df_combined$framework=="Deontology"),]
 
modelo_antroH <- lmer(AntroH ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroH)
 
modelo_mediador_H_agency <- lmer(MoralAgency ~ framework + AntroH + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_H_agency)
 
mediate_test <- mediate(modelo_antroH, modelo_mediador_H_agency, treat = "framework",
    mediator = "AntroH", boot = FALSE, sims = 2000)
summary(mediate_test)
```

#Mediation Analysis Robotization Contractualism vs Utilitarianism
```{r}
#Reliability
df2 <- df_combined[(df_combined$framework=="Contractualism" | df_combined$framework=="Utilitarianism"),]
 
modelo_antroR <- lmer(AntroR ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroR)
 
modelo_mediador_R_reli <- lmer(Reliability ~ framework + AntroR + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_R_reli)
 
mediate_test <- mediate(modelo_antroR, modelo_mediador_R_reli, treat = "framework",
    mediator = "AntroR", boot = FALSE, sims = 2000)
summary(mediate_test)

#Reliability
df2 <- df_combined[(df_combined$framework=="Contractualism" | df_combined$framework=="Deontology"),]
 
modelo_antroR <- lmer(AntroR ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroR)
 
modelo_mediador_R_reli <- lmer(Reliability ~ framework + AntroR + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_R_reli)
 
mediate_test <- mediate(modelo_antroR, modelo_mediador_R_reli, treat = "framework",
    mediator = "AntroR", boot = FALSE, sims = 2000)
summary(mediate_test)

#Reliability
df2 <- df_combined[(df_combined$framework=="Utilitarianism" | df_combined$framework=="Deontology"),]
 
modelo_antroR <- lmer(AntroR ~ framework + acuerdo + (1 | identity),
    data = df2)
sum <- summary(modelo_antroR)
 
modelo_mediador_R_reli <- lmer(Reliability ~ framework + AntroR + acuerdo + (1 | identity),
    data = df2)
summary(modelo_mediador_R_reli)
 
mediate_test <- mediate(modelo_antroR, modelo_mediador_R_reli, treat = "framework",
    mediator = "AntroR", boot = FALSE, sims = 2000)
summary(mediate_test)
```

